---
title: Dynamic report of typical gym goers 
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
library(readr)
```

```{css}
body {
  font-family: Arial, sans-serif;
  background-color: #f4f4f4;
}
h1 {
  color: #2c3e50;
}


```

## Comparison between the number of male and female gymgoers at Cityfitness Ormiston

The plot below shows the number of females vs males gym-goers  from Monday - Friday accross a 2-week period.

```{r}
library(tidyverse)
#unfiltered data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTfad9PEopeQCyBHoPNnajFqsHCx16krDeCBP-0QqZphTZ3jwusKO92dTPPmWoXnaw5MOXrgBojwQNV/pub?output=csv")
logged_data <- logged_data[, -c(1,2)]


#processed data
latest_data <- logged_data %>% rename(weekday = 1,
                                      time_of_day = 2,
                                      cardio = 3,
                                      females = 4,
                                      males = 5,
                                      non_binary = 6,
                                      Total_people = 7)



#plot 1 data
plot1_data <- latest_data %>% 
  select(weekday, males, females, Total_people)


#plot2_data
plot2_data <- latest_data %>% 
  select(weekday, cardio)

#average number of men that go to the gym rounded down
average_men <- floor(latest_data$males %>% sum()/length(latest_data$males))


#average number of women that go to the gym (rounded down)
average_female <- floor(latest_data$females %>% sum()/length(latest_data$females))

#avaerge cardio
avg_cardio <- floor(latest_data$cardio %>% sum()/length(latest_data$cardio))



#average number of people that do cardio
cardio_avg <- floor(latest_data$cardio %>% sum()/length(latest_data$cardio))

#plot 1

plot1_data_long <- plot1_data %>%
  pivot_longer(cols = c("males", "females"), names_to = "Gender", values_to = "Count")






# Plot with males and females as separate bars
ggplot(plot1_data_long, aes(x = factor(weekday, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")), 
                            y = Count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Males vs. Females per Weekday",
       subtitle = "Comparison of gym attendance by gender",
       x = "Weekday",
       y = "Total People")
 
  


#plot with amount of people doing cardio each day
ggplot(plot2_data, aes(x = factor(weekday, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")), 
                       y = cardio)) + 
  geom_bar(stat = "identity", position = "dodge", fill = "purple") + 
  labs(title = "Number of people doing Cardio",
       subtitle = "(includes treadmills, stairmaster, rowing machines, cardio bikes, etc)", 
       x = "Weekday",
       y = "Number of People")

  


```

The average attendance of female gym-goers per period (either evening or morning) is `r average_female` and the average attendance of male gym-goers is `r average_men`. The average number of people doing cardio is 18. 


